\thesistitle

### 2019-04-11 main.tex
Writing some about the state of the art
To be continued

\section{State-of-the-art}
There have been some papers that take some steps towards code clone refactoring.

>>>>

\section{Related work}
There have been some papers that take some steps towards code clone refactoring. Most research towards refactoring code clones has been conducted by Y. Higo et al. In a 2008 study \cite{higo2008metric} the authors look at the refactoring of class-level, method-level and constructor-level clones in Java.
